Glucose ingestion before and after resistance training does not augment ribosome biogenesis in healthy moderately trained young adults

### 2023-03-08 ribose-paper.RMD
updates
results_work updates

@@

###### **Table 1:** Baseline characteristics of the participants. BMI: body mass index, A = charactaristics per sex, B = characteristics per leg. Values are mean ± standard deviation.

@@

![](figures/flowchart_selection.PNG)

###### **Figure 1:** Flowchart of the selection process. The order in which participants performed the two intervention blocks was determined in a planned randomised fashion.

![](figures/timeline.PNG)

###### **Figure 2.** Overview of the intervention, with 12 days of concomitant dietary intervention and resistance training (RT), preceded by 7 days of testing. T0 = timepoint 0 (testing days prior to intervention), T1/T2 = biopsy prior to resistance training for leg #1 and #2, respectively, T3/T4 post intervention testing of leg #1 and #2, respectively, including post sixth RT session. Test = physical performance test (unilateral 1RM leg press, knee extension, isometric knee extension force, isokinetic knee extension torque) testing on days 4, 5, 8, 9, T3, T4 will not include 1RM leg press and knee extension, Biopsy = microbiopsy, RT#1 = resistance training leg #1, RT#2 = resistance training leg#2. Other tests (D2O, DXA, spit) will be conducted as part of the study as a whole. These are not relevant to this data set, thus will not be described here.

@@

###### **Table 2:** Primer sequence and performance. Average cycle thresholds (Ct) and priming efficiencies were calculated from all qPCR reactions.

![](figures/Primer.sequences.PNG)

@@

```{r nutrition change analysis and fig}
# Associated scripts:
# - nut.datahand.R
# - nut.change.R
# - nut.change.figs.R

>>>>

###### **Table 1:**  Baseline characteristics. Age = mean age in years, Height = mean height in cm, Weight and Lean mass = mean in kg, Iso 60/240 = mean unilateral isokinetic knee extension peak torque in Nm at 60 d/s and 240 d/s, Isom = mean unilateral isometric knee extension peak torque in Nm.

![](figures/tab1.png)

@@

@@

@@

@@

```{r nutrition fig}
# Associated scripts:
# - nut.datahand.R
# - nut.change.R
# - nut.change.figs.R
